Github入門

### 2020-01-08 how-to-github.Rmd
update

![](fig/GitHub_gif1.gif)
<br />
<br />
<br />

@@

![](fig/GitHub_fig1.png)

@@

![](fig/GitHub_gif2.gif)
<br />
<br />
<br />

@@

![](fig/GitHub_gif3.gif)
<br />
<br />
<br />

@@

![](fig/GitHub_gif4.gif)
<br />
<br />
<br />

@@

![](fig/GitHub_gif5.gif)
<br />
<br />
<br />

@@

![](fig/GitHub_gif6.gif)
<br />
<br />
<br />

@@

![](fig/GitHub_fig2.png)

>>>>

![](fig/github_gif1.gif)
<br />
<br />
<br />

@@

![](fig/github_fig1.png)

@@

![](fig/github_gif2.gif)
<br />
<br />
<br />

@@

![](fig/github_gif3.gif)
<br />
<br />
<br />

@@

![](fig/github_gif4.gif)
<br />
<br />
<br />

@@

![](fig/github_gif5.gif)
<br />
<br />
<br />

@@

![](fig/github_gif6.gif)
<br />
<br />
<br />

@@

![](fig/github_fig2.png)
